### 2008-05-16 trunk/Papers/dl-gre-08/discussion.tex
minor changes

When we add relations, our algorithm is able to generate 10 of the 15
human-produced relational descriptions correctly (in addition to the
98 non-relational descriptions).  Fig.~\ref{fig:example_outputs} gives
example outputs of the \el\ algorithm for three different orderings,
which together achieve this coverage.  Of the five human-produced
descriptions that the \el\ algorithm cannot generate, three involve
references to sets (\textit{the two blues ones in horizontal
sequence}/\textit{the two yellow drawers}), and two contain so much
redundant information that our algorithm, which similar to the
Incremental Algorithm allows for some redundancy but stops once it has
found a distinguishing description, cannot reproduce them. It does,
however, generate other, simpler descriptions for all of the
human-produced descriptions that cannot be reproduced exactly.

>>>>

When we add relations, our algorithm is able to generate 10 of the 15
human-produced relational descriptions correctly (in addition to the
98 non-relational descriptions).  Fig.~\ref{fig:example_outputs} gives
example outputs of the \el\ algorithm for three different orderings,
which together achieve this coverage.  Of the five human-produced
descriptions that the \el\ algorithm cannot generate, three involve
references to sets (\textit{the two blues ones in horizontal
  sequence}/\textit{the two yellow drawers}), and two contain so much
redundant information that our algorithm cannot reproduce them:
Similarly to the Incremental Algorithm, it allows for some redundancy,
but stops once it has found a distinguishing description. It does,
however, generate other, simpler descriptions for these three
referents. 
%human-produced descriptions that cannot be reproduced exactly.
